Predictive modeling using genomic annotations

### 2018-11-02 Manuscript/manuscript.Rmd
edits

The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions (Aiden et al.). Analyses have shown that the genome is tightly compacted into distinct compartments.  There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) (Dixon et al.). Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD (Symmons et al.). This suggests that the boundaries of TADs may play a role in restricting the function of elements such as enhancers, thereby impacting the transcription of genes. Furthermore, changing the 3D structure of the DNA and distrupting these domains can lead to adverse outcomes and diseases like cancer. Therefore it is important to be able to identify the key molecular drivers of the formation of TADs in order to further our understanding of the human genome.

The mechanisms underlying the formation of TADs are a complex and active area of research. Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangement of higher-order chromatin architecture (Phillips-Cremins et al). Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking. Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long range chromatin contacts (Zuin et al.). Other regulatory elements like DNase I hypersensitive sites, the H3K36 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al). These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription. The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting which epigenomic features are most predictive of the development of TAD boundaries. This will allow us to better understand what leads to their formation.

Due to the size of Hi-C data and the abundance of available genomic features, few methods have been developed to study the role and interplay of different sets of these features on the folding of DNA. Furthermore, many accepted methods ignore key characteristics of the data that, when addressed, may improve predictive performances. One such pitfall is the issue of highly imbalanced classes. The commonality between most accepted methods for predicting TAD boundaries considers performing a classification algorithm by binning the genome and labeling the bins as either containing a TAD boundary or not. However, due to the sparcity of TADs throughout the genome, most bins will not contain a TAD boundary. This will contribute to highly imbalanced classes and has the potential to introduce predictors with near-zero variance. It has been shown that imbalanced classes can result in poor predictive performances of classification algorithms (Blagus et al).  Furthermore, the inclusion of predictors with near-zero variance can add unnecessary noise to the model and decrease computational efficiency of predictive algorithms. Another problem lies in identifying which positional characteristics of the genomic features will optimize prediction. The use of distances (in base pairs) from genomic bins to regions of functional elements has largely been ignored. However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries. Lastly, given that some features tend to colocalize near TAD boundaries, most predictive models may be unable to identify the complete set of features most associated with boundary formation. This can lead to less informative results and restrict our knowledge of how these genomic elements correlate with eachother.

In a previous study (Mourad et al) both a multiple logistic regression model and a LASSO regularized regression model were applied to a wide array of architectural proteins from the GM12878 cell line to predict TAD boundaries. The set of features consisted of whether or not the coordinates of a functional element overlaped with a particular genomic bin (yes or no). In the case of a partial overlap, a percentage of overlap was used. However, the class imbalance issue was not addressed and neither model used is suited to handle multiple correlated predictors. Likewise, it is unclear how the team handled the situation when multiple regions defined by the same genomic element are located within the same bin. The length of the genomic bins can be flexible and as the size increases, there is a greater chance for the occurance of multple regions to be located within the same bin. If a simple indicator (1 or 0) is used, instead of, say, the sum total of regions within that bin, it is possible that a significant amount of information is lost.  Additionally, the team used ROC curves and AUCs to evaluate model performance, which is problematic, especially for highly imbalaned classes (Hanczar et al). A better indicator of predictive performance with classification algorithms is to consider the F1 score and Matthew's Correlation Coefficient (MCC) as they involve all quadrants of a confusion matrix.

In this study we have developed a novel data pre-processing pipeline that addresses the irregularities in the TAD boundary data provided by contact matrices for the GM12878 cell line. We then performed a variety of machine learning algorithms on the pre-processed data to identify the genomic elements that were most predictive of TAD boundaries. Firstly, we found that the models performed on balanced data out performed those on unbalanced data. Secondly, it was determined that multiple iterations of random under-sampling was the balancing technique that yielded the best results. Thirdly, the inclusion of distances as predictors was found to improve model performance compared to a model with simple overlap predictors. Lastly, it was found that performing an inverse normal transformation of the distance predictors further improved model performance.

After applying (insert final model(s)) we were able to confirm that cis-regulatory elements like insulators and promotors were highly predictive of TAD boundaries. The specific transcriptional repressor, CCCTC-binding factor (CTCF), was also found to be highly associated with TAD boundaries. Other non-transcription factor sites like DNase I hypersensitive sites and certain histone modifications like H3K36me3 were also found to be better predictors of TAD boundaries.  Our findings confirm that models with pre-processed data and distance-related genomic features not only perform better, but are also able to correctly identify a range of different functional genomic elements associated with the formation of TAD boundaries. This knowlege will allow us to gain better insight into the role that the spatial organisation of the human genome has on gene regulation.

@@

Publicly available topologically associating domain data was obtained from GEO with accession GSE53525 for the GM12878 cell line (Rao et. al).  The domain data was constructed from in situ Hi-C contact matrices at a 5kb resolution. Identified TAD boundaries were represented by their location in the genome (hg19 human genome assembly), including chromosome, start and end coordinates for chromosomes 1 through 22. The start and end coordinates were concatenated, sorted, and unique coordinates representing the borders demarcating TADs were obtained.

The establishment of the data for modeling first consisted of binning the genome into equal sized intervals. This was performed at the same resolution as the respective cell line. That is, 5 kb genomic bins were used. Next, the boundary coordinates were flanked on either side by 5 kb. A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary. Otherwise, the bin was labeled as not containing a boundary (Y=0). An illustration of the data is presented in Figure X.

@@

Annotation data, in the form of functional genomic coordinates, from ChIP-seq experiments was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium. Similar to Mourad et al. we considered overlaps between bins and regions defined by functional genomic elements when creating the predictor space of our models. If a elemental region was located completely within a bin then the predictor ($X_{i}$) was labeled as 1. If a bin did not overlap with any region then it was labeled as 0. In the case of partial overlaps, a fraction denoting the percent overlap from region to bin was used. However, in contrast to Mourad et al., in the event of multiple regions within the same bin, the sum total of fractions or instances of regions was used as in Figure X.

## DATA PIPELINE

We developed a pipeline that systematically evaluates the problems associated with TAD boundary data in a predictive modeling setting (Figure X). The pipeline addresses X key questions in aiming to improve predictive performances and accurately identify which functional genomic elements are most predictive of TAD boundaries. Prior to initiating the pipeline, predictors with near-zero variances were removed. To identify said predictors, the nearZeroVar function in the CARET package was used. The function considers two metrics. First, the ratio of the most frequent value over the second most frequent value was calculated. Ideally, this ratio would be close to one for well-behaved predictors. Next, the number of unique values divided by the total number of samples multiplied by 100 was calculated. Here, if the frequency ratio was greater than 20 and the percentage of unique values was less than 10, the predictor was flagged as having near-zero variance and removed.

### Class Imbalance

When binning the genome, the sparcity of TAD boundaries contributed to heavily imbalanced classes. That is, proportionally, only a small number of genomic bins overlapped with a flanked TAD boundary. To assess this issue a series of multiple logistic regression models were performed. First, a multiple logistic regression model using the full data with unbalanced classes was assessed. We then compared this to a multiple logistic regression model with balanced classes created by random over-sampling, random under-sampling, and four other multiple logistic regression models with balanced classes created by the SMOTE (Synthetic Minority Over-sampling Technique) function in the DmWR package in R. For each of the random over- and under-sampling methods, multiple iterations were considered up until the difference in the cumulative means reached below a threshold of $5 \times 10^{-5}$. Performances were then aggregated by taking the average across all iterations. It was determined that the model with data untilizing random under-sampling out-performed all other other balancing techniques. However, to this point we only considered overlaps between genomic bins and the regions that defined functional genomic elements.

### Incorporating Distances

To gain further insight into the spatial relationship between these chromatin factors and the genome, we introduced distance predictors into the model. This consisted of the distance from the center of each genomic bin to the center of the nearest region defining a genomic element as depicted in Figure X. To assess any improvement with the inclusion of these predictors we compared the performances of three multiple logistic regression models: one with only the overlap predictors, one with only the aforementioned distance predictors, and one with both.  It was found that the inclusion of distance predictors improved model performance.  Likewise, the model with both types of predictors futher improved model performance. As is common, with genomic data, the use of the distance predictors resulted in highly right skewed data with distances ranging from 0 to tens of thousands in base pairs.

To better improve computational efficiency with regards to the convergence of likelihood maximization, we considered three normalization techniques. The first was a simple $log_{2}$ transformation, in which one was added in the case of distances of 0. The second was an inverse hyperbolic sine tranformation given by $insert function here$ which has the benefit of handling values of 0. Lastly, an inverse normal tranformation was considered. The inverse normal transformation is a way of transforming the sample distribution of a continuous variable to make it appear more normally distributed by matching the normalized rank of the trait to a quantile in a normal distribution using the following formula $insert formula here$. Multiple logistic regression models were performed using data with each respective transformation and compared. It was found that the model with inverse normally transformed distance predictors not only out-performed the other transformation but also out-performed a model with no transformation at all.

### Classification Models

Therefore, the final data used for quantifying the association between each functional genomic element and TAD boundary formation was one that had been balanced using multiple iterations of random under-sampling, incorporated both overlapped and distance predictors, and normalized using an inverse normal transformation. Likewise, prior to model fitting, the predictors were standardized in order to compare magnitudes of the subsequent beta coefficients as a measure of variable importance.  We then performed a wide variety of classification algorithms to determine which genomic elements were most predictive of TAD boundaries. The models included a multiple logistic regression, a multiple logistic regression with both LASSO and Elastic-Net regularization, a random forest, a gradient boosting machine, a support vector machine, and a naiive bayes model. For each model, 10-fold cross validation was performed to tune for any neccessary paramenters. Model performance was compared using F1-scores, MCCs, and AUROCs. The alpha level of significance was set at 0.05. All statistical analyses was performed in R version 3.4.2.

@@

A total of 9048 topologically associating domains and their genomic locations were obtained for the GM12878 cell line for chromosomes 1 through 22.  The median width of TADs was found to be 18.5 kb (IQR: 11.5kb - 33.0kb). The start and end coordiantes of the TADs were translated into a vector of boundary points. There were 1454 (16%) TADs that shared at least one coordinate (start, end, or both) with another TAD. In this case the unique boundary point demarcating two adjacent TADs was considered. The genome was binned at 10 kb interval, resulting in a total of 536396 bins. A total of 536396 genomic bins of 10 kb width were created. After flanking the TAD boundary points on either side by 5 kb, it was found that 31820 (5.9%) bins contained a flanked TAD boundary. We investigated a total of 68 genomic features, 12 (18%) of which were removed because they were assessed as having near-zero variance. Table X presents a full list of the genomic features in addition to the metrics and indicator corresponding to whether or not the feature was to be removed.

## Balancing Classes Improves Performance

It was found that the multiple logistic regression models utilizing random over and under-sampling out-performed the other techniques and were comparatively similar with F1 scores of 0.636 and 0.637 respectively. The under-technique was evaluated over 13 iterations, while the over-sampling technique took far more iterations for the cumulative mean F1 score to converge, X to be exact. Given that and the fact that the under-sampling technique uses significantly less data than the over-sampling, while still performing at the same level, it was concluded that this was the best balancing technique and used in further analyses.

## Incorporating Distance Predictors Improves Performance

The multiple logistic regression model with only distance predictors, evaluated on multiple iterations of random under-sampling was found to improve model performance from 0.637 (using only overlap predictors) to 0.747. Furthermore, the multiple logistic regression model with both types of predictors further improved model performance by raising the F1 score to 0.753. This suggested that the distance predictors were more representative of the association between the genomic elements and TAD boundaries. However, on a genomic scale, distances from the bins to the nearest region defined by a respective genomic element were highly right skewed. We evaluated three tranformations in order to normalize the distance predictors and improve model performance. Out of the three normalization techniques, the multiple logistic regression model with an inverse normal transformation on the distance predictors was found to perform the best with an F1 score of 0.747.

##

>>>>

The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions (Aiden et al.). Analyses have shown that the genome is tightly compacted into distinct compartments.  There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) (Dixon et al.). Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD (Symmons et al.). This suggests that the boundaries of TADs may play a role in restricting the function of elements such as enhancers, thereby impacting the transcription of genes. Furthermore, changing the 3D structure of the DNA and distrupting these domains can lead to adverse outcomes and diseases like cancer. Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.

The mechanisms underlying the formation of TADs are a complex and active area of research. Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangement of higher-order chromatin architecture (Phillips-Cremins et al). Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking. Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long range chromatin contacts (Zuin et al.). Other regulatory elements like DNase I hypersensitive sites, particular histone modifications, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al). These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription. The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting which epigenomic features are most predictive of the development of TAD boundaries. This will allow us to better understand what leads to their formation.

Most accepted methods for predicting TAD boundaries consider performing a classification algorithm by binning the genome and labeling the bins as either containing a TAD boundary or not. However, a pervasive issue becomes the introduction of highly imbalanced classes. Due to the sparcity of TADs throughout the genome, most bins will not contain a TAD boundary. Therefore, the minority class of genomic bins with TAD boundaries in them becomes proportionally smaller than that of the majority class of genomic bins with no TAD boundaries. It is commonly agreed that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate (Estabrooks et al). Furthermore, it is unclear what sized bins best improves predictive performance or even if the results are stable across differently sized genomic bins.

Another problem lies in identifying the feature space of subsequent classification algorithms.  A variety of positional characteristics of the genomic features can be used to describes the relationship between TAD boundaries and genomic elements, but it is unclear which is best. The use of distances (in base pairs) from genomic bins to regions of functional genomic elements has largely been ignored. However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.

In this study we have developed an ensemble framework that aims to address and compare a variety of data irregularities and characteristics that are associated with the prediction of TAD boundaries. We examined the inclusion of three different predictor types as the feature space for predictive modelling. We also examined four resampling techniques aimed at improving class imbalance. Lastly, we examined the effect of three separate variable reduction techniques on model performance. Random forest classification algorithms were performed to investigate which functional genomic features were most associated with the formaton of TAD boundaries. Model performance was evaluated based on a total of four metrics which included test accuracy, area under the ROC curve (AUC), F1 score, and Matthew's Correlation Coefficient (MCC).

[Insert last paragram for introduction]

@@

Publicly available topologically associating domain data was obtained from GEO with accession GSE53525 for the GM12878 cell line (Rao et. al).  The domain data was constructed from in situ Hi-C contact matrices at 5kb, 25kb, 50kb, and 100kb resolutions. Identified TAD boundaries were represented by their location in the genome (hg19 human genome assembly), including chromosome, start and end coordinates for chromosomes 1 through 22. The start and end coordinates were concatenated, sorted, and unique coordinates representing the borders demarcating TADs were obtained.

Figure 1 presents a diagram of how the data was established for modeling purposes. First, the genome was binned into equally sized intervals. This was performed at the same resolution of the contact matrix that the domain data was obtained from. For example, for the domain data obtained from a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals. The same processes was repeated for each of the other three resolutions. Next, the boundary coordinates were flanked on either side by a unit corresponding to the resolution of the particular domain data. Again siting the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb. Again, the same process was repeated for the other three resolutions. A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary. Otherwise, the bin was labeled as not containing a boundary (Y=0).

@@

Annotation data, in the form of functional genomic element, from ChIP-seq experiments was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium. The annotations consisted of a variety of different chromatin states using hidden markov models, histone marks, and DNase I hypersensitive sites. Each annotation is represented by their location throughout the genome via chromosomal coordinates. Using each genomic element we created three types of predictors that were used as features in downstream modelling.

## Ensemble Framework

Figure 2 details the ensemble system proposed and evaluated in this study. For each predictor type chosen, the data, composed of majority and minority classes, was split into a 7:3 ratio of training to testing sets. For the trainig set, a variable reduction technique was performed. The feature space was reduced and a resampling technique was performed. A classification algorithm in the form of a random forest was performed and validated using the test set.

A total of three increasingly refined predictor types where used to describe the relationship between TAD boundaries and each function genomic element of interest. Two different overlap types and a distance type were considered. Figure 3 presents an illustration of each type and is detailed below:

1. Overlap Counts (OC): For each genomic bin, a total count of each overlapped region, defined by a functional genomic element, with a bin was calculated. If no regions overlapped with a bin, then the predictor was assigned as 0.

2. Overlap Percent (OP): For each genomic bin, the percent of overlap between a bin and a region was calculated as the ratio of feature width (in base pairs) and the total width of each bin. Here, the feature width was defined as the number of base pairs that overlapped between a bin and an elemental region. Note, that the denominator of this ratio was given to be that same for each respective domain data used. That is, for the 5kb resolution domain data, the total width of each bin was 5kb.

3. Distance: For each genomic bin, the distance (in base pairs) from the center of the bin to the center of the nearest region of a respective functional genomic elemnt was calculated.

Variable reduction techniques generally fall into one of three main categories: filter methods, wrapper methods, or embedded methods. Filter methods are generally used as a preprocessing step. The selection of features is independent of any machine learning algorithms. Instead, features are selected on the basis of their scores in various statistical tests for their correlation with the outcome variable. In wrapper methods, we try to use a subset of features and train a model using them. Based on the inferences drawn from the previous model, we decide to add or remove features. Embedded methods combine the qualities of filter and wrapper methods by implementing algorithms that have their own built-in feature selection methods.

In this paper, we considered one technique from each group. For a filter method, we performed nonparametric two-sample Kolmogorov–Smirnov tests to assess how different the underlying distributions of a respective genomic element, for each predictor type, were between bins with and with a TAD boundary located inside it. The predictors were sorted according the p-value provided from the test. To determine the suitable number of features to reduce to, we plotted the performance of random forest models when iteratively including a new feature (up to the first 20). For a wrapper method, we performed forward selection. Forward selection is an iterative procedure in which began with an intercept only logistic regression model. At each step a feature is added, defined by a particular predictor type, and the AIC of the model is recorded. The method continues as long as there is a suitable reduction in AIC. Lastly, for an embedded method, we performed LASSO regularized regression. The LASSO regression is a penalization technique that uses L1-norm regularization in logistic regression. Here, the coefficients of irrelevant features are reduced to 0. The subsequent features are chosen for downstream modelling.

To address the class imbalance problem we evaluated four different resampling techniques (in addition to no sampling). For each resampling technique, the majority class is defined as the set of genomic bins that did not include a TAD boundary, while the minority class is defined as the set of bins that included a TAD boundary. The techniques included no sampling, random under-sampling, random over-sampling, SMOTE, and K-Medoids and are disussed in detail below:

1. No Sampling: The full dimension of the training set was used.

2. Random Under-Sampling (RUS): All data points (bins) from the minority class (bins with TAD boundaries) of the training set were used. Data from the majority class (bins without TAD boundaries) are randomly sampled to match the number of minority class instances.  We considered 50 interations, each time randomly sampling from the majority class (without replacement) and performed a separate model. Performance metrics were aggregated by taking the average across all iterations.

3. Random Over-Sampling (ROS): All data points from the majority class of the training set were used. Data from the minority class was randomly sampled (with replacement) to match the size of the majority class instances. Similar to the random under-sampling, we considered 50 iterations and aggregated the results by taking the average.

4. SMOTE (Synthetic Minority Over-Sampling Technique): The method combines both random under-sampling and random over-sampling by creating synthetic observations. The SMOTE algorithm was implemented in R through the DmWR package. The user is able to specify the parameters that control the percent under- and over-sampling. Specific details of the SMOTE algorithm can be found in Chawla et al. For the purposes of this study, the parameters of the algorithm were chosen to create perfectly balanced classes.

5. K-Medoids: This is an unsupervised clustering algorithm. The set of majority classes is isolated and the clustering algorthm is performed. The cluster centers are represented by actual data points. The set of cluster centers are chosen to match the set of minority classes. The final resampled training set is composed of the set of minority classes and the set of cluster centers from the majority classes.

The graphical display of the disparity in classes across the different class-balancing techniques is provided is Figure X. Using set notation the formulation of the ensemble framework can be defined as follows:

Set of Predictor Types:

P = {OC, OP, Distance}

Set of Variable Reduction Techniques:

V = {KS-Test, Forward Selection (AIC), LASSO}

Set of Class-Balancing Methods:

C = {None, RUS, ROS, SMOTE, K-Medoids}

Therefore, given domain data at a specific resolution, a system produced from the ensemble framework is defined as follows:

E = {p, v, c}, where $p \in P$, $v \in V$, and $c \in C$

Once a system was defined, a random forest algorithm was performed using 10-fold cross-validation to reduce bias. Letting $|X|$ denote the cardinality of each set, then for each domain data, we evaluated $|P| \times |V| \times |C|$ different ensemble systems in this paper.

@@

In this section we provide the details of the comprehensive experiments performed in order to assess each ensemble system. For the task of predicting TAD boundaries using functional genomic elements, we used 5 class balancing techniques, and for each balancing technique we used 3 predictor types and 3 variable reduction techniques. We evaluated each ensemble system using 10-fold cross-validated random forest models.
Thus, we generated 45 (=5x3x3) separate models.

After binning the genome at 5kb, [[25kb, 50kb, and 100kb]] there were a total of X [[, X, X, and X]] genomic bins respectively. Table X provides the data distributions of the different classes across each of the balancing techniques. We see that each class balancing technique considered resulted in perfectly balanced classes.

We implemented 3 types of variable reduction techniques that fell into 1 of 3 categories: filter methods, wrapper methods, or embedded methods. For the filter method, we performed nonparametric KS-tests for each predictor in the feature space. P-values of the tests were sorted into increasing order. Figure X presents AUCs and F1 scores results by iteratively adding 1 predictor at a time according to the sorted p-values across each resampling technique. We see that the performances begin to stabilize after the inclusion of the top 15 most significant features. Thus, the top 15 features were selected when applying this filter method for all downstream analyses.

Table X presents the complete results comparing each ensemble system in terms of accuracy, AUC, F1 score, and MCC. We see that the inclusion of distance type predictors significantly improved model performance compared to the other two overlap types. This improvement was apparant across all class balancing techniques. Furthermore, the improvement was irrespective of which variable reduction technique was chosen. Performance metrics remained relatively constant within each model with a specific predictor type and resampling technique, regardless of the variable reduction technique chosen. With respect to the class balancing technique, when isolated to models using distance type predictors, it was found that X preformed best.

Figure X presents the variable importance plot including the top X most predictive functional genomic elements associated with the formation of TAD boundaries. At the top we see X, X, and X
.
.
.
